Verifying Demonstrations

### 2017-08-24 properties.tex
Adds figure illustrating t-poset

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}.
For generality, we will use the terminology of 
\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
structure \iac{tposet}.

@@

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
Then we know that they cannot have been created after the event.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created before end]
    \begin{itemize}
      \item Submit the proof to storage.
      \item The proof must've been created before it was included (duh!).
    \end{itemize}
  \end{idea}
\end{frame}
}

For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
This means that they cannot create a proof and keep it for a future protest.

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the proof.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}.
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
\end{frame}
}

>>>>

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}.
(See \cref{PosetGraph}.)
For generality, we will use the terminology of 
\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
structure \iac{tposet}.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[->,auto,node distance=1.5cm,thick,
    proof node/.style={rectangle,draw},
    time node/.style={circle,draw}]

    \node (prev) {\dots};
    \node[time node] (ts) [right of=prev] {$t_s$};
    \node[proof node] (pA) [right of=ts] {$p_A$};
    \node[proof node] (pB) [below of=pA] {$p_B$};
    \node[time node] (te) [right of=pA] {$t_e$};
    \node (succ) [right of=te] {\dots};

    \path
    (prev) edge node [right] {} (ts)
    (ts) edge node {} (pA)
    (pA) edge node {} (te)
    (ts) edge node {} (pB)
    (pB) edge node {} (te)
    (te) edge node {} (succ);

  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
protest, then the relation will guarantee that \(p_A, p_B\) were created before 
the end of the protest.
Then we know that they cannot have been created after the event.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created before end]
    \begin{itemize}
      \item Submit the proof to storage.
      \item The proof must've been created before it was included (duh!).
      \item If included before \(t_e\), then it was created before \(t_e\).
    \end{itemize}
  \end{idea}
\end{frame}
}

For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
in their proofs, e.g.\ \(t_s\) in \cref{PosetGraph}.
This means that if \(t_s\) is sufficiently close (time-wise) to the protest and 
has sufficiently high entropy, then Alice or Bob cannot create a proof and keep 
it for a future protest.

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval, i.e.\ possibly before the protest.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Created after start]
    \begin{itemize}
      \item Include an unpredictable value in the proof.
      \item This could be e.g.\ the hash of the \enquote{head} of the 
        \ac{tposet}, (\(t_s\) in the figure).
      \item This prevents creating proofs for future protests.
    \end{itemize}
  \end{idea}
\end{frame}
}
